\section*{\sc Key Projects}
\vspace{-2mm}
\hrulefill
\vspace{1mm}

\cventry
{Digital Alpha SaaS Analyser}
{Inter IIT Tech Meet 10.0}
{\texttt{\href{https://docs.google.com/presentation/d/1zgRrYwIt0juemg0FGrPXUjsLX2gD7f9wmv1iU7j4Gxo/edit?usp=sharing}{\faLink{} SaaS-Analyzer}}}
{March 2022}
{
\begin{itemize}
  % Prepared a solution for the High Prep Problem Statement of \textbf{Digital Alpha}, 
  \item Developed a scalable web app and an ML pipeline to analyze SEC filings and obtain SaaS metrics for companies.
  \item \textbf{Parsed} relevant sections (10K, 10Q and 8K) of the SEC Filings using BeautifulSoup and some external APIs.
  \item Extracted SaaS metrics using NER, window search algorithm, used FinBERT (SOTA) to \textbf{analyze sentiments} along with section \textbf{summarization} using legal-pegasus.
  % \item  question-answering model, 
  \item Developed Backend in \textbf{Flask} and \textbf{MongoDB}.
  \item Developed Frontend in \textbf{React}. Gave a modern look to UI using plugins like Chart.js to meet the problem statement.
  \item Won the \textbf{Silver Medal} contributing to the \textbf{overall 2nd position} of IIT Kanpur among 22 IITs.
\end{itemize}
  }
%---------------------------------------------------------
\cventry
  {IITK Coin}
  {Summer Project, Programming Club}
  {\texttt{\href{https://github.com/abhishekshree/iitk-coin}{\faGithub{}}} \texttt{\href{https://github.com/abhishekshree/iitk-coin-native-app}{\faGithub{} IITK-Coin} }}
  {May 2021 - December 2021}
  {
    \begin{itemize}
      \item Developed a Go and React‑Native application for a centralised \textbf{pseudo-currency} system for use in IITK Campus.
      % \item Involved connecting APIs through axios and saving tokens in \textbf{secure-store}. Maintained several application states and navigation between screens.
      \item Built the UI using custom components, axios, secure-store and redux, allowing multiple states and app navigation.
      \item Involved Database Management, User \textbf{Authentication}, Hashing \& Salting and User Session Validation with JWT.
      \item Built robust REST APIs to handle \textbf{concurrent} transactions and multi-level user permissions.
      % , and maintain \textbf{ACID} properties.
    \end{itemize}
  }
  %---------------------------------------------------------
  \cventry
  {MCMC Methods in Julia}
  {Summer Project, Stamatics}
  {\texttt{\href{https://github.com/abhishekshree/mcmc-methods-in-julia}{\faGithub{} MCMC-Methods-in-Julia}}}
  {April 2022 - June 2022}
  {
    \begin{itemize}
      \item Implemented sampling methods including Accept-Reject, Inverse Transform, Importance Sampling, etc.
      \item Learned the mathematics behind Bernoulli Factories, Bayesian Models, MLE, Regression, and Markov Chains.
      \item Implemented MCMC algorithms like Metropolis-Hastings, Gibbs Sampler, portkey Barker’s algorithm, etc.
    \end{itemize}
  }
%---------------------------------------------------------
  \cventry
  {Numbers Made Dumber}
  {Semester Project, Stamatics}
  {\texttt{\href{https://github.com/abhishekshree/Numbers-Made-Dumber}{\faGithub{} Numbers-Made-Dumber}}}
  {April 2021 - July 2021}
  {
    \begin{itemize}
      % \item Worked on understanding algorithms like \textbf{Euclid's Algorithm} and it's immediate consequence like \textbf{Bezout's Identity}, Linear Diophantine Equations, etc.
      % \item Worked on primes like Fermat and Mersenne Primes, \textbf{primality tests} like Lucas–Lehmer Test, Miller-Rabin Test and other similar ideas.
      \item Learned and solved challenging problems about number-theoretic algorithms, prime numbers, and primality tests. Explored cryptography and group theory. 
      \item Implemented the \textbf{RSA} Encryption Algorithm in \textbf{Haskell}.
    \end{itemize}
  }
%   \cventry
%   {Full Stack Web Development}
%   {Semester Project, ACA, IITK}
%   {\texttt{\href{https://github.com/abhishekshree/ACA-FSWD}{\faGithub{} ACA-FSWD}}}
%   {April 2021 - June 2021}
%   {
%     \begin{itemize}
%       \item Learnt HTML, CSS, JavaScript, React, MongoDB, server‑side NodeJS, HTTP Requests \& Headers etc.
%       \item Implemented a front‑end to connect APIs of a mock server using asynchronous JavaScript \& error handling and developed a web app.
%     \end{itemize}
%   }
\vspace{-2mm}

