%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

\cventry
  {With Bhuvan Singla (Y18), Harshit Raj (Y20) and Somya Gupta (Y20)}
  {IITK Coin Frontend Application}
  {\texttt{\href{https://github.com/abhishekshree/iitk-coin-native-app}{\faGithub{} iitk-coin-native-app}}}
  {September 2021 - Present}
  {
    \begin{cvitems}
      \item Developing the frontend application (in React Native) for IITK Coin to be used in IITK campus.
      \item Implemented various components for the app including a secure storage to save JWT tokens received upon login.
      \item Also responsible for integrating and testing the backend APIs with the app for a smooth user experience.
    %   \item
    \end{cvitems}
  }
 \vspace{0.2cm}
%---------------------------------------------------------
  \cventry
  {Mentor: Bhuvan Singla (Y18) | SUMMER PROJECT, PROGRAMMING CLUB}
  {IITK Coin}
  {\texttt{\href{https://github.com/abhishekshree/iitk-coin}{\faGithub{} iitk-coin}}}
  {May 2021 - July 2021}
  {
    \begin{cvitems}
      \item Developed a centralised pseudo-coin system in GoLang for use in IITK Campus.
      \item Built robust REST APIs with multi-level user permissions.
      \item Involved Database Management, Password Authentication with Hashing and Salting and User Session Validation with JSON Web Tokens (JWTs).
      \item Various techniques such as concurrency and deadlock prevention were implemented to keep transactions safe and quick and maintain ACID properties.
    \end{cvitems}
  }
 \vspace{0.2cm}
%---------------------------------------------------------
  \cventry
  {SEMESTER PROJECT, STAMATICS}
  {Numbers Made Dumber}
  {\texttt{\href{https://github.com/abhishekshree/Numbers-Made-Dumber}{\faGithub{} Numbers-Made-Dumber}}}
  {April 2021 - July 2021}
  {
    \begin{cvitems}
      \item Worked on understanding algorithms like Euclid's Algorithm and it's immediate consequence like Bezout's Identity, Linear Diophantine Equations, etc. 
      \item Worked on primes like Fermat and Mersenne Primes, primality tests like Lucas–Lehmer Test, Miller-Rabin Test and other ideas involving primes.
      \item Explored the concepts of Linear and Non-linear congruence, Chinese Remainder Theorem, and its applications.
      \item Explored the ideas involved in cryptography, including group theory. Implemented the RSA Encryption Algorithm as an exercise in Haskell.
    \end{cvitems}
  }
 \vspace{0.2cm}
   
%---------------------------------------------------------
  \cventry
  {SELF PROJECT}
  {Gnix}
  {\texttt{\href{https://github.com/abhishekshree/gnix}{\faGithub{} gnix}}}
  {May 2021}
  {
    \begin{cvitems}
      \item Implemented some basic UNIX Commands like ls, pwd, cat, touch, sleep, whoami, grep (basic search) in golang.
      \item Used Make to automate the build process.
    \end{cvitems}
  }
 \vspace{0.2cm}
%---------------------------------------------------------
  \cventry
  {SELF PROJECT}
  {Handpose Emote Detection}
  {\texttt{\href{https://github.com/abhishekshree/handpose-emote-detection}{\faGithub{} handpose-emote-detection}}}
  {March 2021}
  {
    \begin{cvitems}
      \item Developed a react application which utilized React Webcam to detect hand gestures namely, thumbs up and peace sign.
      \item Read and understood how to mediapipe handpose model works and used it with tensorflow.js.
    \end{cvitems}
  }
 \vspace{0.2cm}
  
%---------------------------------------------------------
  \cventry
  {SELF PROJECT}
  {Android Chat Application}
  {\texttt{\href{https://github.com/abhishekshree/Android-Project}{\faGithub{} Android-Project}}}
  {January 2021}
  {
    \begin{cvitems}
      \item Developed a chat application for android (in Java).
      \item Applied the ideas of Android UI development including different types of views and their life-cycle.
      \item Used firebase auth, storage and database for the backend and integrated them with the application.
    \end{cvitems}
  }
%---------------------------------------------------------
\end{cventries}

